

\documentclass[11pt,a4paper,roman]{moderncv}      
\usepackage[english]{babel}



\moderncvstyle{classic}                            
\moderncvcolor{green}                            

% character encoding
\usepackage[utf8]{inputenc}                     

% adjust the page margins
\usepackage[scale=0.75]{geometry}

% personal data
\name{Qazi Fahim Farhan}{}


\phone[mobile]{01521517207}               
\email{fahim.farhan@outlook.com}                             


\begin{document}

\recipient{To}{Employer}
\date{\today}
\opening{Hello there!}
\closing{Thanks in advance!}
\enclosure[Attachment]{resume}
\makelettertitle


% The first paragraph of your job application letter should include information on why you are writing. 
% Mention the job you are applying for and where you found the position. If you have a contact at the company, 
% mention the person's name and your connection here.

I found the job advertisement on facebook with reference to Dr Anindya Iqbal sir, and 
thought it looked interesting. I therefore apply for "Software Developer - Strategic Dev" at Fiftytwo Digital Ltd. \\

I will not take much of your time, and so I'll go straight into the points. \\
You guys are looking for someone who loves C++ 
which, by the way, is something common in us. I love C++ primarily because I regularly participatte in competitive 
programming contests, such as Codeforces, where one has to use the data structure, 
algorithm and mathematics to solve difficult problems. During my B.Sc course, 
I had done many academic projects, most of which are 
the result of teamwork. So I had to learn how to code in a team and as a result, I came to learn using git and github. 
But again, one has to learn things first which usually means working alone. So yes,
I am comfortable in both , team work and working alone. Sometimes, I get stuck while coding. At those times, I 
look up for the solutions in the error message, stackoverflow, tutorialspoint, geeksforgeeks etc.

I personally think that Windows is genuine for playing and building games using game engine such as CryEngine, Unity, Unreal Engine and so on.
For everything else, there is Linux. It is something that I came to realize when I was in the 3rd year, and 
so I have been using Linux 
(Linux Mint to be precise) for almost two and a half years. It's not Fedora, but I suppose using 'yum' instead of 'apt-get' 
will get half of the job done. I still have Windows for gaming though!

When it comes to learning new languages/frameworks, I usually refer to the official documentation, tutorialspoint or 
some other tutorial site that you randomly come across in Google. Python, Dango, Javascript, C\# are one of those that I learned
on my own from the internet.
 I love using git and so I keep everything in github. And yes, I don't just make commits and push codes in the master branch.
  I create branches of my project and implement new codes in different branches. After reaching a certain checkpoint, I merge the branches with the master and then 
  push it in github. Though I have a lot more to learn on using git.
 
 If you are still reading, I hope you can guess what I am capable of. We both know that you are looking for 
 someone to get the job done. We can certainly help each other out.

% The next section of your cover letter should describe what you have to offer the company. 
% Make strong connections between your abilities and the requirements listed in the job posting. 
% Mention specifically how your skills and experience match the job. Expand on the information in your resume, 
% don't just repeat it.
% Try to support each statement you make with a piece of evidence. 
% Use several shorter paragraphs or bullets rather than one large block of text, 
% which can be difficult to read and absorb quickly.

% Conclude your application letter by thanking the employer for considering you for the position. 
% Include information on how you will follow-up. State that you will do so and indicate when 
% (one week's time is typical). You may want to reduce the time between sending out your resume and follow 
% up if you fax or email it.

Thank you for reading the cover letter. I look forward to hearing from you, and do not hesitate contacting me if you have any questions.

\vspace{0.5cm}


\makeletterclosing

\end{document}
